  ---
title: "Cabbages"
author: "Genevieve Lopez"
date: "September 2020"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
response variable vitamin c is numaric, cultivation methods are categorical   
# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(VitC ~ Cult,data=veggy)
```


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results
```{r}
favstats(VitC ~ Cult,data=veggy)
```

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
the question is there a difference in the vitamin C due to cultivation method?  
$H_0$: there is no difference in vitamin C content due to cultivation.    
$H_A$: there is a difference in vitamin C content due to cultivation.  

```{r}
t.test(VitC ~ Cult,data=veggy)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

It appears from the boxplot that cultivation method C52 results in higher Vitamin C content   
The numerical summary shows that on average C52 cultivation results in about 13 Vitamin C units more.  
The P value is 0.000000003  < 0.05 the null hypothesis is extremly unlikely; we reject the null hypothosis  
We conclude there is a difference in Vitamin C content based on cultivation. 
